Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
put in user

\subsection{User Based and Item Based Recommendation}
Intro to Memory-Based Collaborative Filtering

@@

User-Based Collaborative Filtering

For user-based recommendation, we first calculated the similarity score between every pair of users, u and v, using the equation below:

Inline image 1
\begin{equation}
sim(u,v) = \frac{\# common items}{{\# items(u)}^{1/2} {\# items (v)}^{1/2}}
\end{equation}

Then, for each user, we looked at each song in the dataset and found all other users who have listened to that song. Next, we added up the similarity score of each of those users, v, with the original user, u, and got the weight for a particular song, i:

$w_i = \sum_{v \epsilon V} sim(u, v)$

That sum is a proxy for how likely the user is to like that particular song. We went through that process for all songs and then recommended the user the top 500 songs which had the highest scores. This method led to a MAP value of 0.0383.

Item-Based Collaborative Filtering

For item-based recommendation, which turned out to be our best algorithm in terms of a MAP value, we first calculated the similarity score between every pair of songs, i and j, using the equation below and saved the most similar songs to each song in the process:

Inline image 2

Then, for each user, we found all the songs listened to. Next, we got the most similar songs to each of those songs listened to by the user. If the same similar songs came up multiple times, we added the weights together. In other words, for each song, b, that was found to be similar to one of the songs a that the user listened to, we calculated the score for that song, b:

$w_b = \sum_{a \epsilon A} sim(a, b)$

>>>>

\subsection{User Based and Item Based Collaborative Filtering}
%\subsubsection{Intro to Memory-Based Collaborative Filtering}

@@

\subsubsection{User-Based Collaborative Filtering}

For user-based recommendation, we first calculated the similarity score between every pair of users, $u$ and $v$, using the equation below:

\begin{equation}
sim(u,v) = \frac{\text{\# common items}(u, v)}{{\text{\# items}(u)}^{1/2} \times {\text{\# items}(v)}^{1/2}}
\end{equation}

Then, for each user, we looked at each song in the dataset and found all other users who have listened to that song. Next, we added up the similarity score of each of those users, v, with the original user, u, and got the weight for a particular song, $i$:

$$w_i = \sum_{v \epsilon V} sim(u, v)$$

The sum is a proxy for how likely the user is to like that particular song. We went through that process for all songs and recommended the user the top 500 songs which had the highest scores. This method led to a MAP value of 0.0383.

\subsubsection{Item-Based Collaborative Filtering}

For item-based recommendation, which turned out to be our best algorithm in terms of a MAP value, we first calculated the similarity score between every pair of songs, $i$ and $j$, using the equation below and saved the most similar songs to each song in the process:

\begin{equation}
sim(i,j) = \frac{\text{\# common users}(i, j)}{{\text{\# items}(i)}^{1/2} \times {\text{\# items}(j)}^{1/2}}
\end{equation}

Then, for each user, we found all the songs listened to. Next, we got the most similar songs to each of those songs listened to by the user. If the same similar songs came up multiple times, we added the weights together. In other words, for each song, b, that was found to be similar to one of the songs a that the user listened to, we calculated the score for that song, $b$:

$$w_b = \sum_{a \epsilon A} sim(a, b)$$
